Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-06 paper.tex
Update paper.tex

\subsection*{How was genome-wide diversity impacted by a domestication bottleneck?}
Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$). .
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression at neutral loci from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the domestication bottleneck.

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demographic model, many studies identify domestication loci using a strict outlier approach in which loci showing the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.

@@

Basic:
We're beginning to see the introgression has occurred across a number of crops during their expansion.
What is the genomic architecture of this introgression and does the architecture suggest it's been adaptive?
At what geographic scale is introgression adaptive?  Is it very local?  Do you see different architectures of introgression across different regions?
At what taxonomic scale does introgression occur?  When do species become so diverged that introgression is either not possible or maladaptive?

@@

Applied:
Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is clearly tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.

>>>>

\subsection*{How was genome-wide diversity impacted by a domestication bottleneck?}
Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$).
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression at neutral loci from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the domestication bottleneck.

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demographic model, many studies identify domestication loci using a strict outlier approach in which loci showing the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.
\gmj{This is true in most cases I think, although I remember reading that an opposite pattern was found in sunflowers.  I'll go find that paper again and see if it warrants a mention here.}

@@

\subsection*{Basic:}
We're beginning to see that introgression has occurred across a number of crops during their expansion.
What is the genomic architecture of this introgression and does the architecture suggest that it has been adaptive?
At what geographic scale is introgression adaptive?  Is it very local?  Do you see different architectures of introgression across different regions?
At what taxonomic scale does introgression occur?  When do species become so diverged that introgression is either not possible or maladaptive?

@@

\subsection*{Applied:}
Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is clearly tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.
